CorReg pretreatment : Regression for correlated variables and application in steel industry

### 2014-03-14 www/article13.tex
update numerical results
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@448 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

	\subsection{$Y$ depends on all variables in $X$}	 \label{tableMSEsimtout}	
We first try the method with a response depending on all covariates (\textsc{CorReg} reduces the dimension and can't give the true model if there is a structure). The datasets used here were those from \ref{compZvrai}.
\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$& \psi & indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_51_44.csv
30 & 0 & U& MSE (sd) & 262627.57 (732019) & 5928332.4 (49005690.2) & 262627.57 (732019) \\
& & & cpl (sd) & 30 (0) & 29.99 (0.1) & 30 (0) \\
 &  &HU &MSE (sd) & 262627.57 (732019) & 10381962.64 (90962496.9) & 262627.57 (732019) \\
& & & cpl (sd) & 30 (0) & 30 (0) & 30 (0) \\
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 510747.53 (2287539.8) & 635.42 (335.2) & 610.32 (424.9) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25.06 (0.2) \\
 &  &HU &MSE (sd) & 510747.53 (2287539.8) & 603.24 (415.6) & 610.32 (424.9) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25.06 (0.2) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & 
& & & 
 &  & HU & 
& & & 
\hline
\hline %global50p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_02_25_40.csv
50 & 0 & U&
& & & 
 &  & HU &
& & & 
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	
& & & 
 &  &HU &
& & & 
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&
& & & 
 &  &HU &
& & &
\hline
\hline %global100p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_10_47_32.csv
100 & 0 & U&   \\
& & & \\
 &  &HU &   \\
& & &  \\
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline
\end{tabular} 
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins. When $n<p$ the dataset was reduced to $p=n$ automatically by a $QR$ decomposition as the lm function of R does. Without selection, all models have min$(n,p)$ non-zero coefficients.} \label{YXlinOLS}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  \psi &indicator &LAR  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_51_44.csv
30 & 0 & U&MSE (sd) & 1246.35 (350.5) & 1433.98 (526.7) & 1246.35 (350.5) \\
& & & cpl (sd) & 17.84 (5.5) & 15.79 (5.6) & 17.84 (5.5) \\
 &  &HU &MSE (sd) & 1246.35 (350.5) & 1248.84 (341.4) & 1246.35 (350.5) \\
& & & cpl (sd) & 17.84 (5.5) & 17.63 (5.6) & 17.84 (5.5) \\ \\
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&
& & & 
 &  &HU &
& & & 
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & MSE (sd) & 712.79 (405.2) & 566.32 (226.4) & 554.01 (257.1) \\
& & & cpl (sd) & 16.68 (4.4) & 15.35 (4.3) & 16.14 (4.5) \\
 &  & HU & MSE (sd) & 712.79 (405.2) & 551.92 (242.4) & 554.01 (257.1) \\
& & & cpl (sd) & 16.68 (4.4) & 15.96 (4.4) & 16.14 (4.5) \\
\hline
\hline %global50p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_02_25_40.csv
50 & 0 & U&
& & & 
 &  & HU &
& & & 
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	
& & & 
 &  &HU &
& & & 
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&
& & & 
 &  &HU &
& & &
\hline
\hline %global100p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_10_47_32.csv
100 & 0 & U&   \\
& & & \\
 &  &HU &   \\
& & &  \\
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline
\end{tabular} 
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinLASSO}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  \psi &indicator &Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_51_44.csv
30 & 0 & U&MSE (sd) & 1326.54 (388.4) & 1356.98 (331.4) & 1326.54 (388.4) \\
& & & cpl (sd) & cpl (sd) & 12.14 (5.1) & 12.5 (5.2) & 12.14 (5.1) \\
 &  &HU & MSE (sd) & 1326.54 (388.4) & 1307.96 (356.6) & 1326.54 (388.4) \\
& & & cpl (sd) & 12.14 (5.1) & 12.27 (5.1) & 12.14 (5.1) \\
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 1400.56 (1598.2) & 668.57 (274.6) & 653.59 (283.7) \\
& & & cpl (sd) & 13.86 (6.8) & 14.31 (5.7) & 14.83 (5.3) \\
 &  &HU &MSE (sd) & 1400.56 (1598.2) & 643.25 (277.9) & 653.59 (283.7) \\
& & & cpl (sd) & 13.86 (6.8) & 14.83 (5.6) & 14.83 (5.3) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & 
& & & 
 &  & HU & 
& & & 
\hline
\hline %global50p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_02_25_40.csv
50 & 0 & U&
& & & 
 &  & HU &
& & & 
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	
& & & 
 &  &HU &
& & & 
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&
& & & 
 &  &HU &
& & &
\hline
\hline %global100p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_10_47_32.csv
100 & 0 & U&   \\
& & & \\
 &  &HU &   \\
& & &  \\
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline
\end{tabular} 
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinenet}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
$n$ & $p_2$&  \psi &indicator &Stepwise  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
\hline %global30p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_51_44.csv
30 & 0 & U& MSE (sd) & 1919.43 (861.8) & 2014.13 (683.6) & 1919.43 (861.8) \\
& & &cpl (sd) & 22.8 (3.3) & 19.34 (4.9) & 22.8 (3.3) \\
 &  &HU &MSE (sd) & 1919.43 (861.8) & 1885.39 (814) & 1919.43 (861.8) \\
& & & cpl (sd) & 22.8 (3.3) & 22.73 (3.1) & 22.8 (3.3) \\
\hline %global30p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_49_58.csv
30 & 16 & U&MSE (sd) & 696.46 (492.9) & 662.07 (285.9) & 660.93 (354) \\
& & & cpl (sd) & 15.9 (3.8) & 15.1 (3.7) & 15.76 (3.7) \\
 &  &HU &MSE (sd) & 696.46 (492.9) & 655.94 (325.7) & 660.93 (354) \\
& & & cpl (sd) & 15.9 (3.8) & 15.72 (3.6) & 15.76 (3.7) \\
\hline %global30p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_19_50_41.csv
30 & 32 & U & 
& & & 
 &  & HU & 
& & & 
\hline
\hline %global50p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_02_25_40.csv
50 & 0 & U&
& & & 
 &  & HU &
& & & 
\hline %global50p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_50_48.csv
50 & 16 & U&	
& & & 
 &  &HU &
& & & 
\hline %global50p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_12mars2014_23_49_39.csv
50 & 32 & U&
& & & 
 &  &HU &
& & &
\hline
\hline %global100p40ratio0BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_10_47_32.csv
100 & 0 & U&   \\
& & & \\
 &  &HU &   \\
& & &  \\
\hline %global100p40ratio0.4BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_33_40.csv
100 & 16 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline % global100p40ratio0.8BICTRUEBICstarTRUEp1max5lambda5100Amaxp2max100sigma_sousreg0.001maxit9000maxtry20max_compl1scaleTRUEcandidates-1_13mars2014_04_10_09.csv
100 & 32 & U&  \\
& & &  \\
 &  &HU &  \\
& & & \\
\hline
\end{tabular} 
\caption{Stepwise  combined with constrained \textsc{CorReg}. $Y$ depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinstep}
\end{table}

>>>>

	\subsection{$Y$ depends on all variables in $X$}	 \label{tableMSEsimtout}	
We first try the method with a response depending on all covariates (\textsc{CorReg} reduces the dimension and can't give the true model if there is a structure). The datasets used here were those from \ref{compZvrai}.
\begin{tabular}{|c|c|c|c|c|c|c|}
$n$ & $p_2$& $\psi$ & indicator &OLS  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
30 & 0 & U& MSE (sd) & 262627.57 (732019) & 5928332.4 (49005690.2) & 262627.57 (732019) \\
& & & cpl (sd) & 30 (0) & 29.99 (0.1) & 30 (0) \\
 &  &HU &MSE (sd) & 262627.57 (732019) & 10381962.64 (90962496.9) & 262627.57 (732019) \\
& & & cpl (sd) & 30 (0) & 30 (0) & 30 (0) \\
30 & 16 & U&MSE (sd) & 510747.53 (2287539.8) & 635.42 (335.2) & 610.32 (424.9) \\
& & & cpl (sd) & 30 (0) & 24.11 (1) & 25.06 (0.2) \\
 &  &HU &MSE (sd) & 510747.53 (2287539.8) & 603.24 (415.6) & 610.32 (424.9) \\
& & & cpl (sd) & 30 (0) & 24.82 (0.6) & 25.06 (0.2) \\
30 & 32 & U & MSE (sd) & 178323.95 (1426610.2) & 180.02 (44.9) & 141.03 (27.8) \\
& & & cpl (sd) & 30 (0) & 13.85 (0.9) & 9.27 (0.5) \\
 &  & HU & MSE (sd) & 178323.95 (1426610.2) & 330.31 (134.8) & 141.03 (27.8) \\
& & & MSE (sd) & 178323.95 (1426610.2) & 330.31 (134.8) & 141.03 (27.8) \\
50 & 0 & U&MSE (sd) & 528.08 (228.6) & 886.54 (364.3) & 528.08 (228.6) \\
& & & cpl (sd) & 41 (0) & 36.8 (1.7) & 41 (0) \\
 &  & HU &MSE (sd) & 528.08 (228.6) & 542.29 (235) & 528.08 (228.6) \\
& & & cpl (sd) & 41 (0) & 40.87 (0.4) & 41 (0) \\
50 & 16 & U&MSE (sd) & 612.72 (291.5) & 239.17 (89.4) & 200.32 (42.6) \\	
& & & cpl (sd) & 41 (0) & 24.43 (0.7) & 25.13 (0.4) \\
 &  &HU &MSE (sd) & 612.72 (291.5) & 207.6 (51.3) & 200.32 (42.6) \\
& & & cpl (sd) & 41 (0) & 24.99 (0.5) & 25.13 (0.4) \\
50 & 32 & U&MSE (sd) & 555.44 (262.5) & 128.98 (18.1) & 121.08 (11.9) \\
& & & cpl (sd) & 41 (0) & 11.45 (0.9) & 9.13 (0.3) \\
 &  &HU &MSE (sd) & 555.44 (262.5) & 171.9 (31.1) & 121.08 (11.9) \\
& & &cpl (sd) & 41 (0) & 21 (0) & 9.13 (0.3) \\
100 & 0 & U& MSE (sd) & 167.71 (20.6) & 323.44 (124.1) & 167.71 (20.6) \\
& & & cpl (sd) & 41 (0) & 38.17 (1.3) & 41 (0) \\
 &  &HU &MSE (sd) & 167.71 (20.6) & 167.98 (20.8) & 167.71 (20.6) \\  
& & & cpl (sd) & 41 (0) & 40.99 (0.1) & 41 (0) \\
100 & 16 & U&  MSE (sd) & 168.68 (22.4) & 158.51 (51.6) & 133.49 (12.2) \\
& & & cpl (sd) & 41 (0) & 24.53 (0.7) & 25.08 (0.3) \\
 &  &HU &  MSE (sd) & 168.68 (22.4) & 137.03 (20.3) & 133.49 (12.2) \\
& & & cpl (sd) & 41 (0) & 25.01 (0.4) & 25.08 (0.3) \\
100 & 32 & U&  MSE (sd) & 173.25 (22.9) & 112.8 (10.7) & 110.63 (6.9) \\\\
& & & cpl (sd) & 41 (0) & 10.02 (0.8) & 9.25 (0.5) \\
 &  &HU & MSE (sd) & 173.25 (22.9) & 127.4 (11.9) & 110.63 (6.9) \\
& & & cpl (sd) & 41 (0) & 21 (0) & 9.25 (0.5) \\
\caption{OLS and OLS combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins. When $n<p$ the dataset was reduced to $p=n$ automatically by a $QR$ decomposition as the lm function of R does. Without selection, all models have min$(n,p)$ non-zero coefficients.} \label{YXlinOLS}
\begin{tabular}{|c|c|c|c|c|c|c|}
$n$ & $p_2$&  $\psi$ &indicator &LASSO  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
30 & 0 & U&MSE (sd) & 1246.35 (350.5) & 1433.98 (526.7) & 1246.35 (350.5) \\
& & & cpl (sd) & 17.84 (5.5) & 15.79 (5.6) & 17.84 (5.5) \\
 &  &HU &MSE (sd) & 1246.35 (350.5) & 1248.84 (341.4) & 1246.35 (350.5) \\
& & & cpl (sd) & 17.84 (5.5) & 17.63 (5.6) & 17.84 (5.5) \\ \\
30 &16& U & MSE (sd) & 712.79 (405.2) & 566.32 (226.4) & 554.01 (257.1) \\
& & & cpl (sd) & 16.68 (4.4) & 15.35 (4.3) & 16.14 (4.5) \\
 &  & HU & MSE (sd) & 712.79 (405.2) & 551.92 (242.4) & 554.01 (257.1) \\
& & & cpl (sd) & 16.68 (4.4) & 15.96 (4.4) & 16.14 (4.5) \\
30 & 32 & U & MSE (sd) & 216.12 (128.3) & 157.78 (39.4) & 147.04 (28.4) \\
& & & cpl (sd) & 11.23 (4.4) & 8.56 (1.8) & 7.91 (1.3) \\
 &  & HU & MSE (sd) & 216.12 (128.3) & 178.88 (68.9) & 147.04 (28.4) \\
& & & cpl (sd) & 11.23 (4.4) & 9.86 (3) & 7.91 (1.3) \\
50 & 0 & U&MSE (sd) & 658.38 (221.4) & 872.32 (239.4) & 658.38 (221.4) \\
& & & cpl (sd) & 28.2 (6) & 22.95 (5.8) & 28.2 (6) \\
 &  & HU &MSE (sd) & 658.38 (221.4) & 652.72 (211.9) & 658.38 (221.4) \\
& & & cpl (sd) & 28.2 (6) & 28.36 (5.9) & 28.2 (6) \\
50 & 16 & U&MSE (sd) & 274.34 (101.7) & 268.76 (106.3) & 225.64 (67.5) \\	
& & & cpl (sd) & 22.14 (4.1) & 19.52 (2.9) & 20.47 (2.8) \\
 &  &HU &MSE (sd) & 274.34 (101.7) & 233.8 (78.9) & 225.64 (67.5) \\
& & & cpl (sd) & 22.14 (4.1) & 20.19 (2.8) & 20.47 (2.8) \\
50 & 32 & U&MSE (sd) & 165.6 (73.7) & 128.34 (18.8) & 123.73 (12.8) \\
& & & cpl (sd) & 12.93 (6.4) & 8.51 (1.5) & 8.09 (1.1) \\
 &  &HU &MSE (sd) & 165.6 (73.7) & 135.84 (24.1) & 123.73 (12.8) \\
& & &cpl (sd) & 12.93 (6.4) & 10.17 (3.1) & 8.09 (1.1) \\
100 & 0 & U&  MSE (sd) & 183.33 (31.1) & 357.15 (133.4) & 183.33 (31.1) \\
& & & cpl (sd) & 37.78 (2.4) & 32.93 (3.7) & 37.78 (2.4) \\
 &  &HU &  MSE (sd) & 183.33 (31.1) & 183.78 (31.6) & 183.33 (31.1) \\
& & &  cpl (sd) & 37.78 (2.4) & 37.75 (2.4) & 37.78 (2.4) \\
100 & 16 & U& MSE (sd) & 148.83 (18.6) & 164.44 (54.3) & 139.57 (16.1) \\
& & & cpl (sd) & 25.22 (4) & 21.72 (2) & 22.3 (1.7) \\
 &  &HU &  MSE (sd) & 148.83 (18.6) & 142.97 (22.1) & 139.57 (16.1) \\
& & & cpl (sd) & 25.22 (4) & 22.24 (1.8) & 22.3 (1.7) \\
100 & 32 & U& MSE (sd) & 124.29 (19.9) & 113.36 (11) & 111.54 (7.2) \\
& & & cpl (sd) & 13.18 (5.9) & 8.68 (1.2) & 8.53 (1) \\
 &  &HU & MSE (sd) & 124.29 (19.9) & 118.33 (12) & 111.54 (7.2) \\
& & & cpl (sd) & 13.18 (5.9) & 11.02 (2.9) & 8.53 (1) \\
\caption{LASSO (with LAR) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinLASSO}
\begin{tabular}{|c|c|c|c|c|c|c|}
$n$ & $p_2$&  $\psi$ &indicator &Elasticnet  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
30 & 0 & U&MSE (sd) & 1326.54 (388.4) & 1356.98 (331.4) & 1326.54 (388.4) \\
& & & cpl (sd) & 12.14 (5.1) & 12.5 (5.2) & 12.14 (5.1) \\
 &  &HU & MSE (sd) & 1326.54 (388.4) & 1307.96 (356.6) & 1326.54 (388.4) \\
& & & cpl (sd) & 12.14 (5.1) & 12.27 (5.1) & 12.14 (5.1) \\
30 & 16 & U&MSE (sd) & 1400.56 (1598.2) & 668.57 (274.6) & 653.59 (283.7) \\
& & & cpl (sd) & 13.86 (6.8) & 14.31 (5.7) & 14.83 (5.3) \\
 &  &HU &MSE (sd) & 1400.56 (1598.2) & 643.25 (277.9) & 653.59 (283.7) \\
& & & cpl (sd) & 13.86 (6.8) & 14.83 (5.6) & 14.83 (5.3) \\
30 & 32 & U & MSE (sd) & 855.74 (582.6) & 181.08 (51.9) & 146.79 (32.7) \\
& & & cpl (sd) & 15.57 (6.3) & 11.19 (2.4) & 8.37 (1.3) \\
 &  & HU & MSE (sd) & 855.74 (582.6) & 311.57 (163.9) & 146.79 (32.7) \\
& & & cpl (sd) & 15.57 (6.3) & 14.87 (3.9) & 8.37 (1.3) \\
50 & 0 & U&MSE (sd) & 738.94 (254.5) & 914.56 (283.7) & 738.94 (254.5) \\
& & & cpl (sd) & 25.85 (8.7) & 20.97 (7.8) & 25.85 (8.7) \\
 &  & HU &MSE (sd) & 738.94 (254.5) & 751.06 (262.2) & 738.94 (254.5) \\
& & & cpl (sd) & 25.85 (8.7) & 25.43 (8.8) & 25.85 (8.7) \\
50 & 16 & U&	MSE (sd) & 516.36 (226.6) & 276.6 (133.6) & 228.85 (89.3) \\
& & & cpl (sd) & 26.72 (7.4) & 20.49 (3.8) & 21.8 (3.3) \\
 &  &HU &MSE (sd) & 516.36 (226.6) & 239.77 (103.7) & 228.85 (89.3) \\
& & & cpl (sd) & 26.72 (7.4) & 21.57 (3.4) & 21.8 (3.3) \\
50 & 32 & U&MSE (sd) & 328.7 (146.3) & 130.61 (20.6) & 124.01 (15.4) \\
& & & cpl (sd) & 24.7 (7.1) & 9.95 (1.5) & 8.22 (1.2) \\
 &  &HU &MSE (sd) & 328.7 (146.3) & 169.13 (40.2) & 124.01 (15.4) \\
& & &cpl (sd) & 24.7 (7.1) & 16.04 (3.8) & 8.22 (1.2) \\
100 & 0 & U& MSE (sd) & 175.93 (25.9) & 355.79 (143.8) & 175.93 (25.9) \\
& & & cpl (sd) & 39.71 (1.7) & 34.11 (4.6) & 39.71 (1.7) \\
 &  &HU &  MSE (sd) & 175.93 (25.9) & 176.2 (26.3) & 175.93 (25.9) \\
& & &  cpl (sd) & 39.71 (1.7) & 39.69 (1.7) & 39.71 (1.7) \\
100 & 16 & U&  MSE (sd) & 173.65 (25.1) & 164.96 (59) & 139.51 (17.6) \\
& & &  cpl (sd) & 35.54 (4.2) & 22.58 (2.2) & 23.26 (1.9) \\
 &  &HU &  MSE (sd) & 173.65 (25.1) & 143.04 (23.2) & 139.51 (17.6) \\
& & & cpl (sd) & 35.54 (4.2) & 23.16 (1.9) & 23.26 (1.9) \\
100 & 32 & U&  MSE (sd) & 161.92 (25.2) & 113.61 (10.9) & 111.46 (7.2) \\
& & &  cpl (sd) & 30.78 (6.4) & 9.25 (1.2) & 8.67 (1) \\
 &  &HU &  MSE (sd) & 161.92 (25.2) & 127.44 (13.3) & 111.46 (7.2) \\
& & &cpl (sd) & 30.78 (6.4) & 17.85 (2.7) & 8.67 (1) \\
\caption{Elasticnet (with Elasticnet) combined with constrained \textsc{CorReg}.$Y$  depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinenet}
\begin{tabular}{|c|c|c|c|c|c|c|}
$n$ & $p_2$&  $\psi$ &indicator &Stepwise  &    \textsc{CorReg} $\hat S$& \textsc{CorReg} $S$\\ 
30 & 0 & U& MSE (sd) & 1919.43 (861.8) & 2014.13 (683.6) & 1919.43 (861.8) \\
& & &cpl (sd) & 22.8 (3.3) & 19.34 (4.9) & 22.8 (3.3) \\
 &  &HU &MSE (sd) & 1919.43 (861.8) & 1885.39 (814) & 1919.43 (861.8) \\
& & & cpl (sd) & 22.8 (3.3) & 22.73 (3.1) & 22.8 (3.3) \\
30 & 16 & U&MSE (sd) & 696.46 (492.9) & 662.07 (285.9) & 660.93 (354) \\
& & & cpl (sd) & 15.9 (3.8) & 15.1 (3.7) & 15.76 (3.7) \\
 &  &HU &MSE (sd) & 696.46 (492.9) & 655.94 (325.7) & 660.93 (354) \\
& & & cpl (sd) & 15.9 (3.8) & 15.72 (3.6) & 15.76 (3.7) \\
30 & 32 & U & MSE (sd) & 394.93 (356) & 155.18 (36.4) & 147.81 (30.3) \\
& & &cpl (sd) & 16.1 (6.3) & 8.26 (1.7) & 7.77 (1.3) \\
 &  & HU &  MSE (sd) & 394.93 (356) & 189.49 (79) & 147.81 (30.3) \\
& & & cpl (sd) & 16.1 (6.3) & 10.23 (3) & 7.77 (1.3) \\
50 & 0 & U&MSE (sd) & 745.88 (241.7) & 962.12 (319.3) & 745.88 (241.7) \\
& & & cpl (sd) & 27.19 (4.6) & 22.9 (4.5) & 27.19 (4.6) \\
 &  & HU &MSE (sd) & 745.88 (241.7) & 749.08 (244.2) & 745.88 (241.7) \\
& & & cpl (sd) & 27.19 (4.6) & 27.21 (4.5) & 27.19 (4.6) \\
50 & 16 & U&	MSE (sd) & 279.82 (151.1) & 290.13 (117.3) & 239.61 (69.5) \\
& & & cpl (sd) & 21.24 (5.2) & 18.13 (2.8) & 19.23 (2.7) \\
 &  &HU &MSE (sd) & 279.82 (151.1) & 252.35 (108.5) & 239.61 (69.5) \\
& & & cpl (sd) & 21.24 (5.2) & 18.97 (2.7) & 19.23 (2.7) \\
50 & 32 & U&MSE (sd) & 199.3 (158.7) & 126.81 (17.4) & 124.19 (13) \\
& & & cpl (sd) & 14.31 (6.2) & 8.16 (1.2) & 8.04 (1) \\
 &  &HU &MSE (sd) & 199.3 (158.7) & 136.32 (25.2) & 124.19 (13) \\
& & &cpl (sd) & 14.31 (6.2) & 9.59 (2.6) & 8.04 (1) \\
100 & 0 & U&   MSE (sd) & 193.26 (34.9) & 387.18 (151.6) & 193.26 (34.9) \\
& & & cpl (sd) & 36.3 (2.5) & 30.94 (4.2) & 36.3 (2.5) \\
 &  &HU &   MSE (sd) & 193.26 (34.9) & 194.43 (37.3) & 193.26 (34.9) \\
& & &  cpl (sd) & 36.3 (2.5) & 36.22 (2.7) & 36.3 (2.5) \\
100 & 16 & U&  MSE (sd) & 145.46 (20.1) & 165.74 (56.1) & 140.27 (17.5) \\
& & & cpl (sd) & 23.44 (3.8) & 21.23 (2.1) & 21.93 (1.7) \\
 &  &HU &  MSE (sd) & 145.46 (20.1) & 143.74 (23.2) & 140.27 (17.5) \\
& & & cpl (sd) & 23.44 (3.8) & 21.86 (1.7) & 21.93 (1.7) \\
100 & 32 & U& MSE (sd) & 128.44 (18.4) & 113.27 (10.7) & 111.77 (7.2) \\
& & &  cpl (sd) & 13.58 (5.2) & 8.59 (1.1) & 8.48 (1) \\
 &  &HU &  MSE (sd) & 128.44 (18.4) & 118.61 (11.5) & 111.77 (7.2) \\
& & & cpl (sd) & 13.58 (5.2) & 10.75 (2.8) & 8.48 (1) \\
\caption{Stepwise  combined with constrained \textsc{CorReg}. $Y$ depends on all variables in $X$. \textsc{CorReg} logically wins}\label{YXlinstep}
